An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-17 neurips-19/poly-embed.tex
top-k edit

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
Observe that this is like $\elltop{2}$, with a punishment for reporting weight on elements of $r$ other than the outcome and a reward for showing a ``higher confidence'' in the correct outcome (i.e. $r_y = 2$).
Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.

>>>>

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.

Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.
